
\begin{sidewaystable}[!h]
    \centering
    \small
   \begin{tabularx}{22cm}{|p{2.5cm}|p{2.5cm}|p{3.5cm}|X|p{3.5cm}|p{2.5cm}|}
   \hline
   Authors & Application & FE mesh & Material models & Boundary conditions & Stress-free config. \\
\hline
  Azar F. et al. \citep{azar_methods_2002} &  Computer assisted breast surgery & 8-Node hexahedrons (trilinear isotropic elements) & Skin-elastic linear, 
   adipose,glamdular-hyperelastic polynomial & Sliding between breast - thorax and breast-paddle & Prone breast geometry\\
   \hline
 Rajagopal V. et al.  \citep{rajagopal_modelling_2007} & Breast compression & 8-Node hexahedrons (tricubic Hermite elements)& Homogeneous , Neo-Hookean model& Zero-displacement BC & Buoyant breast in water \\
   \hline
  Pathmanathan P. et al. \citep{pathmanathan_predicting_2008}&Image registration & 8-Node hexahedrons (trilinear elements)& Homogeneous breast-polynomial hyperelastic; Skin exponential hyperelastic  & Zero-displacement on muscle; Compression with imposed displacement & Inverse FE algorithm \\
   \hline
  Han L. et al. \citep{han_nonlinear_2014}& Image registration& 4-Node tetrahedrons & Muscle, glandular, fatty, skin - Neo-Hookean model & Sliding on pectoral muscle & Inverse gravity \\
   \hline
 Gamage T. et al.  \citep{gamage_modelling_2012}&  Computer assisted breast surgery & 8-Node hexahedrons (tricubic Hermite elements) & Homogeneous+ muscle- Neo-Hookean incompressible model& Zero-displacement BC on rib cage surface, Sternum, axilla ends, shoulder & PC iterative algorithm \\
   \hline
 Patete P. et al.  \cite{patete_multi_2013}& Computer assisted breast surgery& 4-Node tetrahedrons (trilinear isotropic elements) & Adipose , glandular, skin & Zero-displacement BC on the  chest wall&PC iterative algorithm\\
   \hline
 Kuhlmann M. et al. \citep{kuhlmann_mechanical_2013}& image registration & 4-Node tetrahedrons & Adipose, glandular- linear gel-like (Eulerian formulation); Skin - hyperelastic material (Lagrangian formulation) & Zero-displacement chest wall& PC iterative algorithm\\
   \hline
   
 Georgii J. et al.  \citep{georgii_simulation_2016}&Surgery simulation & 8-Node hexahedrons, 2-node 3D spars & homogeneous elastic material, Cooper's ligaments-generic mass-spring model & sliding BC (breast on the pectoral muscle) & NA\\
   \hline
  Eiben B. et al. \citep{eiben_surface_2016} & Surgery outcome prediction & 4-Node tetrahedrons & Fatty , glandular- Neo-Hookean model; skin- exponential hyperelastic & Zero-displacement BC & Inverse FE algorithm \\ 
   \hline
  Garcia E. et al. \citep{garcia_mapping_2017} & 3D breast lesion localization & 4-Node tetrahedrons & adipose, glandular  - Neo-Hookean models &zero-displacement BC & Prone breast configuration\\
   \hline
    \end{tabularx}
     \caption{Breast biomechanical models}
     \label{table:mechanical_models_table}
\end{sidewaystable}


%\end{table}